Business Analytics 1 : Finding Groups Within the Data

### 2015-12-02 1_finding_groups/finding_groups.Rmd
half done

---
title: "Business Analytics 1 : Finding Groups Within the Data"
author: "Ming-Yu Liu"
output: 
  html_document: 
    number_sections: yes
    theme: united
    toc: yes
---

@@

Let's read in the dataset to get a feel of what it looks like, before going further.

@@

- group 3 : SKUs with high sales and high variability. We'll call them "white bulls", because despite of its possible high sales, it is difficult to control. These SKUs will be treated on a case by case basis. Things may be a bit difficult to anticipate, but their returns may be high.

@@

When presenting the upper result table, one visualization you can use is the radar chart. However since the current version of the ggplot2 library still does not support actual radar chart with a simple function call (as least not to my knowledge) and each variable of the data is recorded with different scales, therefore, the visualization after using the max-min normalization method may look a bit hacky, as with this normalization, there will be values of 0 ( A different kind of normalization is used here because the scale function produces negative numbers and that does not sound very intuitive for radar charts ).

@@

This wraps up our example of where clustering algorithms can be used to improve your businesses efficiency. You can find all the code to this documentation [here](https://github.com/ethen8181/Business-Analytics/blob/master/1_finding_groups/finding_groups.R).

>>>>

---
title: "Business Analytics 1 : Finding Groups Within the Data"
author: "Ming-Yu Liu"
date: "November 11, 2015"
output: 
  html_document: 
    number_sections: yes
    theme: united
    toc: yes
---

@@

Let's read in the dataset to get a feel of what it looks like, before going further. Oh, and the link to the datasets used in this documentation is located at the bottom of the report.

@@

- group 3 : SKUs with high sales and high variability. We'll call them "wild bulls", because despite of its possible high sales, it is difficult to control. These SKUs will be treated on a case by case basis. Things may be a bit difficult to anticipate, but their returns may be high.

@@

When presenting the upper result table, one visualization you can use is the radar chart. However since the current version of the ggplot2 library still does not support actual radar chart with a simple function call (as least not to my knowledge) and each variable of the data is recorded with different scales. Therefore, the visualization after using the max-min normalization method on the recorded score may look a bit hacky ( the `scale` function produces negative numbers and that does not sound very intuitive for radar charts, thus a different kind of normalization is used here ). As with this normalization, there will be values of 0.

@@

This wraps up our example of where clustering algorithms can be used to improve your businesses efficiency. You can find all the code (finding_groups.R) and datasets (in the data folder) used in this documentation [here](https://github.com/ethen8181/Business-Analytics/tree/master/1_finding_groups).

Any comments or suggestions is appreciated. That includes bugs or typos report. You can file these new issues [here](https://github.com/ethen8181/Business-Analytics/issues).
